### 2014-03-15 src/analysis.Rnw
Turn off graphs other than sample(x)

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")

o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")

o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")

o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel$operators <- 16 - o.xp.opsel$operators
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"

>>>>

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.sample <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp.sample, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type) + myopts + theme(legend.position="none") + opts(title="sample(x)")
# o.xp.round <- subset(o.processed, grepl('^r[.].*.m[.]red',ind))
# ggplot(subset(o.xp.round, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type)+ myopts+ theme(legend.position="none")+ opts(title="sample(x)")
# 
# o.loc.ext <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
# ggplot(subset(o.loc.ext, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(external)")
# 
# o.loc.int <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
# ggplot(subset(o.loc.int, reduction < 100), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="loc(internal)")
# 
# o.one <- subset(o.processed, grepl('^o[.].*.m[.]red',ind))
# ggplot(subset(o.one, reduction < 100 & (type=='line' | type=='method')), aes(power, reduction, fill=interaction(type,power), dodge=type)) +
#   stat_boxplot(geom ='errorbar')+
#   geom_boxplot() + facet_wrap(~type) + myopts+ theme(legend.position="none") + opts(title="One per element")
@
\caption{The effect of sampling reductions, Except for line sampling of power $5$ and $6$ all others are above 0.90 $R^2$.}
\label{fig:xroundsel}
\end{figure*}

\begin{figure*}[t]
<<op.sample,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp.opsel <- o.op.processed
o.xp.opsel$operators <- 16 - o.xp.opsel$operators
colnames(o.xp.opsel)[colnames(o.xp.opsel)=="operators"] <- "rm.operators"
